| Base de datos de abejas ibéricas \n| Iberian bees database\n

### 2022-04-25 Manuscript/manuscript.Rmd
Final edits and changes

output:
  pdf_document: default
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: Ecosistemas_template.docx
csl: ecosistemas.csl
bibliography:
- references.bib
- knitcitations.bib
editor_options:

  chunk_output_type: console
header-includes:
- \DeclareUnicodeCharacter{0301}{*************************************}
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \captionsetup[table]{labelformat=empty}
- \usepackage{orcidlink}

>>>>

output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: Ecosistemas_template.docx
  pdf_document: default
csl: ecosistemas.csl
bibliography:
- references.bib
- knitcitations.bib
editor_options:

  chunk_output_type: console
header-includes:
- \DeclareUnicodeCharacter{0301}{*************************************}
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \captionsetup[table]{labelformat=empty}
- \usepackage{orcidlink}
---
